### 2020-06-22 Report/aws_325ghz_study.tex
tables for DoF

\begin{table}[!b]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-31  & 165.500 & 2800\\
    AWS-32  & 176.311 & 2000\\
    AWS-33  & 178.811 & 2000\\
    AWS-34  & 180.311 & 1000\\
    AWS-35  & 181.511 & 1000\\
    AWS-36  & 182.311 & \phantom{0}500\\
    AWS-4X  & 229.000 & 2000\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    ICI-5  & 325.15$\pm$9.50 & 3000\\
    ICI-6  & 325.15$\pm$3.50 & 2400\\
    ICI-7  & 325.15$\pm$1.50 & 1600\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Fixed channel position and widths. The left table covers channels of
    AWS, with values taken from SoW. Channels AWS-31 to AWS-36 are at this
    moment mandatory for AWS, while AWS-4X is so far tentative. The right table
    lists the values of some channels of ICI \citep{eriksson:towar:20}.}
  \label{tab:fixed:chs}
\end{table}

@@

>>>>

\begin{table}[!b]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-21  &  89.*** & 4000\\
    AWS-31  & 165.500 & 2800\\
    AWS-32  & 176.311 & 2000\\
    AWS-33  & 178.811 & 2000\\
    AWS-34  & 180.311 & 1000\\
    AWS-35  & 181.511 & 1000\\
    AWS-36  & 182.311 & \phantom{0}500\\
    AWS-4X  & 229.000 & 2000\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    ICI-5  & 325.15$\pm$9.50 & 3000\\
    ICI-6  & 325.15$\pm$3.50 & 2400\\
    ICI-7  & 325.15$\pm$1.50 & 1600\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Fixed channel position and widths. The left table covers channels of
    AWS, with values taken from SoW. Channels AWS-31 to AWS-36 are at this
    moment mandatory for AWS, while AWS-4X is so far tentative. The right table
    lists the values of some channels of ICI \citep{eriksson:towar:20}.}
  \label{tab:fixed:chs}
\end{table}

@@

\section{Degrees of freedom}
%

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c}
		 325\,GHz & \multicolumn{3}{c}{DoF}   \\
		 option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
		\hline
		three-a &                8 &                7 &                7 \\
		three-b &                8 &                8 &                6 \\
		four    &                8 &                7 &                6 \\
		\hline
	\end{tabular}
	\caption{The degrees of freedom for AWS with 325\,GHz channel. Both clear and cloudy cases are considered. Results for all three options of 325\,GHz and different $T_r$ are shown.    }
	\label{tab:DoF:all}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c}
	325\,GHz & \multicolumn{3}{c}{DoF}   \\
	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
	\hline
	three-a &                7 &                7 &                5 \\
	three-b &                7 &                6 &                4 \\
	four    &                6 &                5 &                4 \\
	\hline
\end{tabular}
	\caption{Same as Table~\ref{tab:DoF:all}, but only for clear cases.}
\label{tab:DoF:clear}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c}
	325\,GHz & \multicolumn{3}{c}{DoF}   \\
	option &  $T_r = 1200 $\,K &   $T_r = 1800 $\,K &   $T_r = 2400$\,K \\
		\hline
		three-a &                8 &                8 &                8 \\
		three-b &                8 &                8 &                8 \\
		four    &                8 &                8 &                8 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:DoF:all}, but only for cloudy cases.  }
	\label{tab:DoF:cloudy}
\end{table}

\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c}
		&   DoF \\
		\hline
		all    &      6        \\
		clear  &      6        \\
		cloudy &      6        \\
		\hline
	\end{tabular}
	\caption{The degrees of freedom for AWS with 229\,GHz channel. }
	\label{tab:DoF:4X}
\end{table}
